---
title: "p8105_hw5_wy2369"
output: github_document
date: "2022-11-13"
author: Wenjing Yang
---

```{r, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

# Problem 2

### Read and clean

Using the code chunk to read and clean data from `homicide-data.csv`

```{r}
homicide_data = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names()
```

### Describe the raw data

In the raw data, there are **`r nrow(homicide_data)`** rows and **`r ncol(homicide_data)`** columns. It contains **`r ncol(homicide_data)`** important variables which are uid (`uid`), dates of report (`reported_date`), last and first names of victim (`victim_last`and `victim_first`), race of victim (`victim_race`), age of victim (`victim_age`), sex of victim (`victim_sex`), variables of location (`city`, `state`, `lat` and `lon` ), and the status of case (`disposition`) from 50 large cities in the U.S.

### Create a `city_state` variable

Using mutate function to create a new variable. 

```{r}
homicide_df = 
  homicide_data %>% 
  mutate(city_state = str_c(city, ",", state)) 
```

### Find the total number of homicides within cities.

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  count(city_state) %>% 
  summarize(n) %>%
  knitr::kable()
```

From this table, we could find the total number of homicides within 51 cities not 50, and there is one uncommon data from **Tulsa,AL**. Since I know **Tulsa,AL** does not exist in the U.S, we should probably ignore this data from `homicide_df` dataset. 

### Find the number of unsolved homicides

```{r}
tidy_homicide_df = 
  homicide_df %>% 
  filter(city_state != "Tulsa,AL") %>% 
  mutate(
    homicide_status =  ifelse(disposition != "Closed by arrest", "unsolved", "solved")
  )

tidy_homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(homicide_status == "unsolved"),
    total_homicides = n()) %>% 
  knitr::kable()
```

From this table, we could find the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

### Use the `prop.test` function to estimate the proportion of homicides that are unsolved

```{r}

```


