---
title: "p8105_hw5_wy2369"
output: github_document
date: "2022-11-13"
author: Wenjing Yang
---

```{r, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

# Problem 2

### Read and clean

Using the code chunk to read and clean data from `homicide-data.csv`

```{r}
homicide_data = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names()
```

### Describe the raw data

In the raw data, there are **`r nrow(homicide_data)`** rows and **`r ncol(homicide_data)`** columns. It contains **`r ncol(homicide_data)`** important variables which are uid (`uid`), dates of report (`reported_date`), last and first names of victim (`victim_last`and `victim_first`), race of victim (`victim_race`), age of victim (`victim_age`), sex of victim (`victim_sex`), variables of location (`city`, `state`, `lat` and `lon` ), and the status of case (`disposition`) from 50 large cities in the U.S.

### Create a city_state variable

(e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).


